\documentclass[9.5pt, a4paper]{article}

% ── Page geometry ──────────────────────────────────────────────────────────────
\usepackage[left=1.2cm, right=1.2cm, top=1.1cm, bottom=1.1cm]{geometry}

% ── Typography ─────────────────────────────────────────────────────────────────
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{palatino}

% ── Utilities ──────────────────────────────────────────────────────────────────
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage{hyperref}
\usepackage{xcolor}

% ── Colours ────────────────────────────────────────────────────────────────────
\definecolor{accent}{RGB}{26, 82, 118}
\definecolor{subtle}{gray}{0.45}
\definecolor{rulecol}{gray}{0.80}

% ── Hyperlink style ────────────────────────────────────────────────────────────
\hypersetup{colorlinks=true, urlcolor=accent, linkcolor=accent}

% ── Global spacing ─────────────────────────────────────────────────────────────
\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}

% ── List settings ──────────────────────────────────────────────────────────────
\setlist[itemize]{noitemsep, topsep=1pt, parsep=0pt, partopsep=0pt,
                  leftmargin=1.3em, label=\textcolor{accent}{\textbullet}}

% ── Section header ─────────────────────────────────────────────────────────────
\newcommand{\cvsection}[1]{%
  \vspace{4pt}%
  {\color{accent}\textbf{\MakeUppercase{#1}}}\\[-5pt]
  {\color{rulecol}\rule{\linewidth}{0.5pt}}%
  \vspace{1pt}%
}

% ── Experience entry: inline bullet, no extra list env ─────────────────────────
\newcommand{\entry}[4]{%   {Title}{Org}{Date}{One-line bullet}
  \textbf{#1} \textbar\ \textit{#2}\hfill{\small\color{subtle}#3}\\
  {\small #4}%
}

% ── Project entry ──────────────────────────────────────────────────────────────
\newcommand{\project}[3]{%  {Name}{Stack}{One-line bullet}
  \textbf{#1} {\small\color{subtle}\textit{— #2}}\\
  {\small #3}%
}

\pagestyle{empty}

% ══════════════════════════════════════════════════════════════════════════════
\begin{document}

% ── Header ─────────────────────────────────────────────────────────────────────
\begin{center}
  {\Large\textbf{Shaan Shoukath}}\\[3pt]
  \small
  \href{mailto:shaanshoukath4522@gmail.com}{shaanshoukath4522@gmail.com}
  \;|\; (+91) 9061553544
  \;|\; \href{https://www.linkedin.com/in/shaan-shoukath-04a9b12b2/}{LinkedIn}
  \;|\; \href{https://github.com/Shaan-Shoukath}{GitHub}
  \;|\; Kochi, India
\end{center}

% ── Summary ────────────────────────────────────────────────────────────────────
\cvsection{Summary}
{\small EEE student (CGPA: 8.04, CUSAT 2023--27) with hands-on experience in embedded systems, IoT, autonomous robotics, and full-stack web development. Skilled in Linux-based development, hardware--software co-design, and AI-driven systems.}

% ── Technical Skills ───────────────────────────────────────────────────────────
\cvsection{Technical Skills}
\begin{tabularx}{\linewidth}{@{} l @{\hspace{6pt}} X @{}}
  \small\textbf{Languages}  & \small C, C++, Embedded C, Python, Verilog HDL, SystemVerilog, JavaScript, SQL, HTML, CSS \\
  \small\textbf{Web / App}  & \small React, Next.js, Node.js, Express.js, Flask, Django, Flutter, MongoDB, Supabase, PostgreSQL \\
  \small\textbf{Hardware}   & \small Raspberry Pi, ESP32, Arduino, NodeMCU, 8051, FPGA (Xilinx), IMU, GNSS, Ultrasonic, LDR \\
  \small\textbf{Tools / ML} & \small ROS2, OpenCV, TensorFlow, NumPy, Matplotlib, Git, MySQL, wrf-python, NetCDF4 \\
  \small\textbf{OS}         & \small Linux (Ubuntu, Arch, Raspberry Pi OS), macOS, Windows \\
\end{tabularx}

% ── Experience ─────────────────────────────────────────────────────────────────
\cvsection{Professional Experience}

\entry{Tech Associate Head}{EESA, CUSAT}{Jul 2025 – Present}%
      {Leading full-stack development with Next.js and Django; overseeing technical architecture and deployment.}

\vspace{3pt}
\entry{Student Intern – MEP Systems}{Voltech Group}{May – Jun 2025}%
      {Studied HVAC, electrical distribution, and plumbing schematics; exposure to load estimation and safety standards.}

\vspace{3pt}
\entry{Tech Team Member}{SEDS CUSAT}{2025 – Present}%
      {Contributing to MERN-stack projects and technical event infrastructure.}

\vspace{3pt}
\entry{Front-End Developer Intern}{Oxpel India Technologies}{May 2024}%
      {Built responsive UIs with React and Tailwind CSS; integrated REST APIs and managed version control via Git.}

% ── Projects ───────────────────────────────────────────────────────────────────
\cvsection{Selected Projects}

\project{Multi-Drone Agricultural System (Arkairo)}{ROS2 · ArduPilot · MAVLink · Raspberry Pi 5 · Cube Orange+}%
        {Autonomous dual-drone system with drone-to-drone MAVLink telemetry; KML path planning, PID visual servoing, and precision spray control validated in SITL.}
        
\vspace{3pt}
\project{Aarannu — Community Digital ID Platform}{React · Express · Supabase · PostgreSQL}%
        {Full-stack ID management with QR verification, bulk PDF/ZIP generation, and RLS-secured storage.}

\vspace{3pt}
\project{FruiteForest — Gamified Productivity App}{Flutter · Dart}%
        {Cross-platform focus timer with reward-based gamification and persistent progress tracking.}

\vspace{3pt}
\project{Tinkerbluds — Cultivated Land Validation}{GEE · Sentinel-1/2 · XGBoost · FastAPI · Supabase}%
        {Fused NDVI, SAR, SRTM, and ESA WorldCover to classify farmland; ML-based PASS/REVIEW/FAIL pipeline with crop plausibility scoring via REST API.}

\vspace{3pt}
\project{Kaffe — AI Branding \& Content Studio}{FastAPI · React · Multi-Agent · GPT-4o · Gemini}%
        {Multi-agent system converting product images into SEO blogs, captions, and social posts via parallel orchestrated workflows.}


% ── Education & Certifications ─────────────────────────────────────────────────
\cvsection{Education \& Certifications}
\begin{tabularx}{\linewidth}{@{} X r @{}}
  \small\textbf{B.Tech., Electrical and Electronics Engineering} & \small\textbf{CGPA: 8.04} \\
  \small Cochin University of Science and Technology (CUSAT) & \small 2023 – 2027 \\[3pt]
  \small\href{https://coursera.org/share/be953313c178bdf0ee8309b2a82b541a}{\textbf{Deep Learning Specialization}} — Coursera / DeepLearning.AI \small{\color{subtle}(Andrew Ng · Neural Networks, CNNs, Sequence Models, Optimization)} & \\
\end{tabularx}

% ── Community ──────────────────────────────────────────────────────────────────

\cvsection{Community \& Volunteering}
\textbf{Volunteer}, TinkerHub (May 2025–Present): delivered Flutter workshop to 100+ students; mentored projects and hosted technical sessions.}

\vspace{3pt}

{\small\textbf{Inventory Manager}, TinkerSpace (Jan 2026–Present): hardware inventory and equipment logistics for prototyping.\quad


\end{document}