\documentclass[10.8pt, a4paper]{article}

% ── Page geometry ──────────────────────────────────────────────────────────────
\usepackage[left=1.1cm, right=1.1cm, top=1.0cm, bottom=1.0cm]{geometry}

% ── Typography ─────────────────────────────────────────────────────────────────
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{palatino}

% ── Utilities ──────────────────────────────────────────────────────────────────
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage{hyperref}
\usepackage{xcolor}

% ── Colours ────────────────────────────────────────────────────────────────────
\definecolor{accent}{RGB}{26, 82, 118}
\definecolor{subtle}{gray}{0.45}
\definecolor{rulecol}{gray}{0.80}

% ── Hyperlink style ────────────────────────────────────────────────────────────
\hypersetup{colorlinks=true, urlcolor=accent, linkcolor=accent}

% ── Global spacing ─────────────────────────────────────────────────────────────
\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}

% ── List settings ──────────────────────────────────────────────────────────────
\setlist[itemize]{noitemsep, topsep=1pt, parsep=0pt, partopsep=0pt,
                  leftmargin=1.3em, label=\textcolor{accent}{\textbullet}}

% ── Section header ─────────────────────────────────────────────────────────────
\newcommand{\cvsection}[1]{%
  \vspace{7pt}%
  {\color{accent}\textbf{\MakeUppercase{#1}}}\\[-5pt]
  {\color{rulecol}\rule{\linewidth}{0.5pt}}%
  \vspace{2pt}%
}

% ── Experience entry ───────────────────────────────────────────────────────────
\newcommand{\entry}[4]{%   {Title}{Org}{Date}{One-line bullet}
  \textbf{#1} \textbar\ \textit{#2}\hfill{\small\color{subtle}#3}\\
  {\small #4}%
}

% ── Project entry ──────────────────────────────────────────────────────────────
\newcommand{\project}[5]{%  {Name}{Stack}{Bullet1}{Bullet2}{GitHubURL}
  \textbf{#1} {\small\color{subtle}\textit{— #2}}\ifx&#5&\else\hfill{\small\href{#5}{\textcolor{accent}{GitHub}}}\fi\\
  {\small #3}%
  \ifx&#4&\else\\ {\small #4}\fi%
}

\pagestyle{empty}

% ══════════════════════════════════════════════════════════════════════════════
\begin{document}

% ── Header ─────────────────────────────────────────────────────────────────────
\begin{center}
  {\Large\textbf{Shaan Shoukath}}\\[3pt]
  \small
  \href{mailto:shaanshoukath4522@gmail.com}{shaanshoukath4522@gmail.com}
  \;|\; (+91) 9061553544
  \;|\; \href{https://www.linkedin.com/in/shaan-shoukath-04a9b12b2/}{LinkedIn}
  \;|\; \href{https://github.com/Shaan-Shoukath}{GitHub}
  \;|\; Kochi, India
\end{center}

% ── Summary ────────────────────────────────────────────────────────────────────
\cvsection{Summary}
{\small An adaptive and curious student with a passion for tinkering with ideas and building them into working prototypes. Driven by a genuine interest in researching emerging technologies and creating across domains — from autonomous robotics and embedded systems to full-stack web applications and AI-driven tools. Thrives at the intersection of hardware and software, technology-agnostic and comfortable picking up whatever tool best fits the problem, always looking for the next challenge worth solving.}

% ── Education ──────────────────────────────────────────────────────────────────
\cvsection{Education}
\begin{tabularx}{\linewidth}{@{} X r @{}}
  \small\textbf{B.Tech., Electrical and Electronics Engineering} & \small\textbf{CGPA: 8.04} \\
  \small Cochin University of Science and Technology (CUSAT) & \small 2023 – 2027 \\
\end{tabularx}

% ── Technical Skills ───────────────────────────────────────────────────────────
\cvsection{Technical Skills}
\begin{tabularx}{\linewidth}{@{} l @{\hspace{6pt}} X @{}}
  \small\textbf{Languages}  & \small C, C++, Embedded C, Python, Verilog HDL, SystemVerilog, JavaScript, SQL, HTML, CSS \\
  \small\textbf{Web / App}  & \small React, Next.js, Node.js, Express.js, FastAPI, Django, Flutter, MongoDB, Supabase, PostgreSQL \\
  \small\textbf{Hardware}   & \small Raspberry Pi, ESP32, Arduino, NodeMCU, 8051, FPGA (Xilinx), IMU, GNSS, Ultrasonic, LDR \\
  \small\textbf{Tools / ML} & \small ROS2, OpenCV, TensorFlow, NumPy, Matplotlib, Git, MySQL, wrf-python, NetCDF4 \\
  \small\textbf{OS}         & \small Linux (Ubuntu, Arch, Raspberry Pi OS), macOS, Windows \\
\end{tabularx}

% ── Experience ─────────────────────────────────────────────────────────────────
\cvsection{Professional Experience}

\entry{Front-End Developer Intern}{Oxpel India Technologies}{May 2024}%
      {Built responsive UIs with React and Tailwind CSS; integrated REST APIs and managed version control via Git.}

\vspace{4pt}
\entry{Student Intern – MEP Systems}{Voltech Group}{May – Jun 2025}%
      {Studied HVAC, electrical distribution, and plumbing schematics; exposure to load estimation and safety standards.}

\vspace{4pt}
\entry{Community Mentor \& Inventory Manager}{TinkerSpace}{Jan 2026 – Present}%
      {Mentoring student projects and hosting technical sessions; managing hardware inventory and equipment logistics for prototyping.}

% ── Projects ───────────────────────────────────────────────────────────────────
\cvsection{Selected Projects}

\project{Multi-Drone Agricultural System (Arkairo)}{ROS2 · ArduPilot · MAVLink · Raspberry Pi 5 · Cube Orange+}%
        {Autonomous dual-drone system with drone-to-drone MAVLink telemetry, KML-based path planning, and precision spray control.}%
        {Implemented PID visual servoing for crop-row tracking; full workflow validated in SITL simulation before field deployment.}%
        {https://github.com/Shaan-Shoukath/ROS-Arkairo}

\vspace{4pt}
\project{Aarannu — Community Digital ID Platform}{React · Express · Supabase · PostgreSQL}%
        {Full-stack identity management with QR-code verification, bulk PDF/ZIP export, and row-level-security–enforced cloud storage.}%
        {Handled end-to-end deployment including schema design, auth flows, and admin dashboard for community operators.}%
        {https://github.com/Shaan-Shoukath/Aarannu}

\vspace{4pt}
\project{FruiteForest — Gamified Productivity App}{Flutter · Dart}%
        {Cross-platform focus timer with reward-based gamification, streak tracking, and persistent progress storage across sessions.}%
        {Implemented state management and animated UI transitions to deliver a polished mobile experience on both iOS and Android.}%
        {https://github.com/Shaan-Shoukath/FruiteForest}

\vspace{4pt}
\project{Tinkerbluds — Cultivated Land Validation}{GEE · Sentinel-1/2 · XGBoost · FastAPI · Supabase}%
        {Fused NDVI, SAR, SRTM, and ESA WorldCover features to classify farmland parcels with ML-based PASS/REVIEW/FAIL scoring.}%
        {Built a REST API serving crop plausibility predictions; integrated geospatial pipeline end-to-end from satellite ingestion to dashboard.}%
        {https://github.com/Shaan-Shoukath/Tinkerbluds}

\vspace{4pt}
\project{Kaffe — AI Branding \& Content Studio}{FastAPI · React · Multi-Agent · GPT-4o · Gemini}%
        {Multi-agent system that converts product images into SEO-optimised blog posts, ad captions, and platform-specific social content.}%
        {Designed parallel orchestration layer to run independent agent workflows concurrently, cutting generation latency by ~60\%.}%
        {https://github.com/Shaan-Shoukath/Kaffe}

% ── Community ──────────────────────────────────────────────────────────────────
\cvsection{Community \& Volunteering}
{\small\textbf{Tech Volunteer}, EESA CUSAT (Jul 2025–Present): contributed to the EESA CUSAT website; assisted with full-stack development using Next.js and Django.}

\vspace{4pt}
{\small\textbf{Tech Team Member}, SEDS CUSAT (2025–Present): built the ID card generation backend using Node.js and MongoDB; contributing to MERN-stack projects and technical event infrastructure.}

\vspace{4pt}
{\small\textbf{Volunteer}, TinkerHub (May 2025–Present): delivered Flutter workshop to 100+ students; mentored projects and hosted technical sessions.}

% ── Certifications ─────────────────────────────────────────────────────────────
\cvsection{Certifications}
{\small\href{https://www.coursera.org/account/accomplishments/specialization/D2GSDEZHMNFZ}{\textbf{Deep Learning Specialization}} — Coursera / DeepLearning.AI \hfill {\color{subtle}Andrew Ng · Neural Networks, CNNs, Sequence Models, Optimization}}

\end{document}