\documentclass[10pt,a4paper]{article}

\usepackage[left=1.5cm,right=1.5cm,top=2cm,bottom=2.2cm]{geometry} \usepackage{setspace} \setstretch{1.08}

\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{url}
\usepackage{enumitem}
\usepackage{palatino}
\usepackage{tabularx}
\fontfamily{SansSerif}
\usepackage{hyperref}
\selectfont

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\usepackage{color}
\definecolor{mygrey}{gray}{0.82}
\raggedbottom

\setlength{\tabcolsep}{0in}
\newcommand{\isep}{-2 pt}
\newcommand{\lsep}{-0.5cm}
\newcommand{\psep}{-0.6cm}
\renewcommand{\labelitemii}{$\circ$}

\pagestyle{empty}
%-----------------------------------------------------------
% Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\small \colorbox{mygrey}{\begin{minipage}{0.99\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[3]{
\begin{tabular*}{6.62in}{l @{\extracolsep{\fill}} r}
	\textsc{{\textbf{#1}}} & \textsc{\textit{[#2]}} \\
\end{tabular*}\vspace{-8pt}}
%-----------------------------------------------------------

\begin{document}

% Blank white space for the header to be added by placement team
%   \hspace{0.1em}\\ % also use up a newline
%   \vspace{2.7cm}\\ % the remaining free space.

% Dummy header is written here, just for example in between the tags:  \iffalse and \fi .. 
% \iffalse 
\begin{table}
    \begin{minipage}{0.15\linewidth}
        \centering
    \end{minipage}
    \begin{minipage}{1.65\linewidth}
        \setlength{\tabcolsep}{20pt}
        \def\arraystretch{1.15}
        \begin{tabular}{ll}
            \textbf{\Large{Shaan Shoukath}}   \\
            LinkedIn Profile: 
            \href{https://www.linkedin.com/in/shaan-shoukath-04a9b12b2/}
            {Shaan-Shoukath}\\
            GitHub:
            \href{https://github.com/Shaan-Shoukath}
            {Shaan-Shoukath}\\
            Email: 
            \href{mailto:shaanshoukath4522@gmail.com} {shaanshoukath4522@gmail.com}  \\
            Contact: {(+91)9061553544} \\
        \end{tabular}
    \end{minipage}\hfill
\end{table}    

\setlength{\tabcolsep}{5pt}

\begin{table}
\centering
\begin{tabular}{llll}
\toprule
\textbf{Education} & \textbf{Institute} & \textbf{Year} & \textbf{CGPA/Status} \\ 
\toprule
B.Tech.,Electrical And Electronics & Cochin University Of Science And Technology, Kochi & 2023–27 & 8.04 \\
\bottomrule
\end{tabular}
\end{table}


\noindent
\resheading{\textbf{CAREER OBJECTIVE}}\\[-0.4cm]
\begin{itemize}
\item Electrical and Electronics Engineering student with a strong foundation in electronics, IoT systems, and AI-driven embedded solutions. Experienced in Linux-based development and hardware–software co-design. Passionate about building scalable, power-efficient, and intelligent systems that bridge real-world sensing with smart decision-making.
\end{itemize}

\noindent
\resheading{\textbf{PROFESSIONAL EXPERIENCE}}\\[-0.4cm]
\begin{itemize}[noitemsep,nolistsep]

\item \textbf{Front-End Web Developer Intern} | \textbf{\emph{Oxpel India Technologies}} \hfill \emph{May 2024}
\begin{itemize}[noitemsep]
    \item Developed responsive web interfaces using \textbf{React, JavaScript, HTML, CSS, and Tailwind CSS}.
    \item Built reusable UI components and integrated frontend logic with backend APIs.
    \item Managed feature updates and version control workflows using \textbf{Git}.
    \item Improved cross-device compatibility and layout responsiveness across web pages.
\end{itemize}

\item \textbf{Student Intern – MEP Systems} | \textbf{\emph{Voltech Group}} \hfill \emph{May 2025 – Jun 2025}
\begin{itemize}[noitemsep]
    \item Gained practical exposure to \textbf{Mechanical, Electrical, and Plumbing (MEP)} system design and execution workflows.
    \item Studied HVAC layouts, electrical distribution systems, and plumbing schematics through technical drawings.
    \item Observed on-site implementation processes and system coordination practices.
    \item Developed understanding of load estimation principles and safety standards.
\end{itemize}


\end{itemize}

\noindent
\resheading{\textbf{TECHNICAL SKILLS}}\\[-0.4cm]
\begin{itemize}[noitemsep,nolistsep]

    \item \textbf{Programming Languages:} C, C++, Embedded C, Python, Verilog HDL, SystemVerilog, SQL, JavaScript, HTML, CSS.
    
    \item \textbf{Frontend \& Full-Stack:} React, Next.js, Flutter, Node.js, Express.js, Flask, MongoDB, Supabase.
    
    \item \textbf{Hardware Platforms:} Raspberry Pi, ESP32, Arduino, NodeMCU, 8051 Microcontroller, FPGA (Xilinx), Sensors and Actuators (IMU, GNSS, Ultrasonic, LDR, etc.)
    
    \item \textbf{Tools \& Frameworks:} ROS2, OpenCV, TensorFlow, NumPy, Matplotlib, NetCDF4, wrf-python, MySQL, Git.
    
    \item \textbf{Operating Systems:} Linux (Ubuntu, Arch, Raspberry Pi OS), macOS, Windows.
    
    \item \textbf{Domains of Interest:} Embedded Systems, Autonomous Systems, Linux Systems, App Development, Web Development, Machine Learning, Data Science, Deep Learning, Computer Vision, Data Visualization.

\end{itemize}

\noindent
\resheading{\textbf{CERTIFICATIONS}}\\[-0.4cm]
\begin{itemize}[noitemsep,nolistsep]

    \item \href{https://coursera.org/share/be953313c178bdf0ee8309b2a82b541a}
    {\textbf{Deep Learning Specialization}} \hfill Coursera (DeepLearning.AI) \\
    \textit{Instructor: Andrew Ng} \\
    Neural Networks, CNNs, Sequence Models, Optimization, Regularization, Hyperparameter Tuning

    \vspace{4pt}

    \item \href{https://upskill.tutedude.com/certificate/TD-SHAA-ML-1351}
    {\textbf{Machine Learning Certification}} \hfill Tutedude \\
    Supervised \& Unsupervised Learning, Regression, Classification, Model Evaluation

    \vspace{4pt}

    \item \href{https://upskill.tutedude.com/certificate/TD-SHAA-DC-1347}
    {\textbf{Data Science Certification}} \hfill Tutedude \\
    Data Cleaning, Exploratory Data Analysis, Visualization, Pandas, NumPy

\end{itemize}


\noindent
\resheading{\textbf{POSITIONS OF RESPONSIBILITY}}\\[-0.1cm]
\begin{itemize}[noitemsep,nolistsep]

\item \textbf{Tech Associate Head} | \textbf{\emph{EESA, CUSAT}} \hfill \emph{Jul 2025 – Present}
\begin{itemize}[noitemsep]
    \item Leading full-stack development initiatives using \textbf{Next.js and Django}; overseeing technical architecture and deployment workflows.
\end{itemize}

\item \textbf{Tech Team Member} | \textbf{\emph{SEDS CUSAT}} \hfill \emph{2025 – Present}
\begin{itemize}[noitemsep]
    \item Contributing to MERN-stack based development projects and technical event infrastructure.
\end{itemize}

\item \textbf{Inventory Manager – Makerspace} | \textbf{\emph{TinkerSpace}} \hfill \emph{2025 – Present}
\begin{itemize}[noitemsep]
    \item Managing hardware inventory, component tracking, and equipment logistics for prototyping activities.
\end{itemize}

\item \textbf{Volunteer} | \textbf{\emph{TinkerHub}} \hfill \emph{May 2025 – Present}
\begin{itemize}[noitemsep]
    \item Delivered a one-day Flutter workshop for 100+ students, introducing cross-platform mobile app development fundamentals.
    \item Mentored student projects and hosted technical sessions at TinkerSpace to support hands-on learning and prototyping.
\end{itemize}
\end{itemize}


\end{itemize}

\noindent
\resheading{\textbf{SELECTED PROJECTS}}\\[-0.1cm]
\begin{itemize}[noitemsep,nolistsep]

\item \textbf{Multi-Drone Agricultural System (Arkairo)}  
\textit{ROS 2 · ArduPilot · MAVLink · Raspberry Pi 5 · Cube Orange+}  
\begin{itemize}[noitemsep]
    \item Engineered a fully autonomous dual-drone system with direct drone-to-drone MAVLink telemetry (GCS-free operation).
    \item Implemented KML-based path planning, geotag transmission, PID visual servoing, and precision spray control; validated in SITL.
\end{itemize}

\item \textbf{EESA CUSAT Official Website}  
\textit{Next.js · Django · PostgreSQL}  
\begin{itemize}[noitemsep]
    \item Developed and deployed the official departmental website with modules for notes, events, gallery, and member management.
    \item Implemented REST API integration between Next.js frontend and Django backend.
\end{itemize}

\item \textbf{Aarannu — Community Digital ID Platform}  
\textit{React · Express · Supabase · PostgreSQL}  
\begin{itemize}[noitemsep]
    \item Built a full-stack ID management platform with QR verification, bulk PDF/ZIP generation, and RLS-secured storage.
\end{itemize}

\item \textbf{Raspberry Pi 5 NAS with RAID-1}  
\textit{Linux · mdadm · Samba · OpenMediaVault}  
\begin{itemize}[noitemsep]
    \item Developing a RAID-1 network storage system with automated backups and cross-platform file sharing.
\end{itemize}

\item \textbf{FruiteForest — Gamified Productivity App}  
\textit{Flutter · Dart}  
\begin{itemize}[noitemsep]
    \item Developed a cross-platform focus timer app integrating reward-based gamification and persistent progress tracking.
\end{itemize}

\end{itemize}
\noindent
\resheading{\textbf{IDEATHON ENTRIES \& PROTOTYPE SUBMISSIONS}}\\[-0.1cm]
\begin{itemize}[noitemsep,nolistsep]

\item \textbf{Kaffe — AI Branding \& Content Studio}  
\textit{FastAPI · React · Multi-Agent Systems · GPT-4o · Gemini}  
\begin{itemize}[noitemsep]
    \item Developed a multi-agent AI system that transforms uploaded product images into SEO blogs, captions, and marketing strategies.
    \item Designed orchestrated agent workflows with parallel execution and automated social media publishing.
\end{itemize}

\item \textbf{Tinkerbluds — Cultivated Land Validation Platform}  
\textit{Google Earth Engine · Sentinel-1/2 · XGBoost · FastAPI · Supabase}  
\begin{itemize}[noitemsep]
    \item Built a satellite-data fusion system combining NDVI, SAR (VH/VV), terrain (SRTM), and ESA WorldCover to classify agricultural land.
    \item Implemented ML-based PASS/REVIEW/FAIL validation, crop plausibility scoring, and REST API-based plot verification.
\end{itemize}

\end{itemize}

\vspace{0.2cm}

\vspace{0.2cm}

\noindent
\resheading{\textbf{SELF DECLARATION}}\\[-0.4cm]
\begin{itemize}[leftmargin=*]
    \item I hereby declare that the information provided above is true and correct to the best of my knowledge and belief.
\end{itemize}

\begin{center}
    {\footnotesize \textit{As of February 2026}}
\end{center}

\end{document}
